%main

\documentclass{article}

\usepackage{geometry} \usepackage{graphicx} \usepackage{amsmath}
\usepackage{listings} \usepackage{multirow} \usepackage{fancyhdr}

\pagestyle{fancy} \fancyhf{} \rhead{Dina Elreedy, Chen Liu, Hang Yan,
  Hao Yan} \lhead{CSE 427 Final Project Report} \cfoot{\thepage}

\title{CSE 427 final project report\\ Netflix user rating prediction
  with collaborative filtering}

\author{Dina Elreedy, Chen Liu, Hang Yan, Hao Yan}

\begin{document}
\maketitle
\section{Introduction and motivation}
Recommender Systems are used in diverse applications. Online markets
recommend products to customer that they may be interested in buying;
social networks recommend friends or pages; online streaming services
(e.g. Netflix) recommand movies to users. 

Recommender systems are significant since companies can improve their
sales using accurate recommender systems. Additionally, using
recommender systems enhances customer satisfaction especially when
he/she feels that the recommendations made by the system match their
taste or needs to a great extent. Accordingly, both customers and
companies would got some benefit from using recommender systems.

In this project we tackled the problem of predicting the ratings for
movies from a set of users, which will guide the recommender system to
recommend movies that matches his/her interest. Formally, given a set
of $n$ users and $k$ movies and an incomplete rating matrix $U$ of $n$
by $k$ entries, where $U_{ij}$ represents the rating from user $i$ to
the movie $j$, our task is to predict the missing entries of $U$. The
prediction is made possible with a large set of training data,
consisting the incomplete rating of other $m$ users for the same set
of $k$ movies.

There are multiple ways to solve this problem. The algorithm we are
using is collaborative filtering, which takes the idea from $kth$
nearest neighbor search (KNN). Given a user and the movie whose rating
we want to predict, we first find similar users/movies in the training
set that have the ratings on this movie, then predict the unknown
rating from these known ratings. The core of the algorithm is to find
similar users/movies with the testing user/movie in the training
set. Given the scale of the problem, we implemented our algorithm with
Spark and MapReduce and execute it on the real cloud platform.

%% This project works on a subset of Netflix challenge dataset, which is
%% a real dataset for a big data application. So we were interested in
%% applying big data tools such as: Spark for preprocessing data analysis
%% and Java Map Reduce for the main algorithm on a real cluster
%% environment to solve such a real interesting big data application.
\input{preprocessing.tex}

\input{implementation.tex}

\input{cloud.tex}

\input{result.tex}

\section{Conclusion}
In this project, we have developed a system that predicts missing
ratings of a movie for a user using collaboarative filtering approach which helps in recommendation systems as these ratings can guide the company like Netflix which movies to recommend to which users. First, we have analyzed the data using Spark and designed the algorithm based on this analysis results. Then, the collaboarative filtering algorithm is implemented with MapReduce framework and executed on Microsift Azure Hdinsight service. We have also improved the original collaboarative filtering and the prediction algorithm to balance the prediction accuracy and number of predicted entries. Experimental results demonstrate the effectiveness of our system and show the impact of several parameters.
\input{groupwork.tex}
\end{document}
